---
params:
    save: NULL #"first.Rda"
    load: "first.Rda"
    completeReload: false
# bibliography: CohortDefinition.bib
# csl: nature-publishing-group-vancouver.csl
output:
  pdf_document:
    keep_tex: true
    md_extensions: +raw_attribute
    latex_engine: xelatex
mainfont: Arial    
fontsize: 11pt
geometry: margin=1in
classoptions: doublespace
longtable: true
header-includes:
  - \usepackage[numbers,sort&compress]{natbib}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{caption}
  - \usepackage{rotating}
  - \usepackage{multirow}
  - \usepackage{mwe,tikz}
  - \usepackage[percent]{overpic}
  - \usepackage{enumitem}
  - \usepackage{mas_fun}
  - \usepackage{hyperref}
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage[table]{xcolor}', x, fixed = TRUE)})
library(dplyr)
library(tidyr)
library(xtable)
library(gridExtra)
library(cowplot)

readRdsCamelCase <- function(file) {
  result <- readRDS(file)
  colnames(result) <- SqlRender::snakeCaseToCamelCase(colnames(result))
  return(result)
}
```

\centerline{{\Huge Supplementary Material}}
\vspace{1.0em}
\centerline{\Large for}
\vspace{1.0em}
\centerline{\huge Renin-angiotensin system blockers and}
\centerline{\huge susceptibility to COVID-19}
\vspace{1.0em}
\centerline{\Large by}
\vspace{1.0em}
\centerline{\Large Daniel R. Morales, Mitchell M. Conover, Seng Chan You, et al.}
<!-- \centerline{\Large Seng Chan You, RuiJen Chen, Nicole Pratt, Christian G. Reich,} -->
<!-- \centerline{\Large Jon Duke, David Madigan, George Hripcsak and Patrick B.Ryan} -->

\tableofcontents

\captionsetup[table]{name=Supplementary Table}
\captionsetup[figure]{name=Supplementary Figure}
\captionsetup{labelfont=bf}

\renewcommand\theContinuedFloat{\alph{ContinuedFloat}}

```{r, echo=FALSE}
cohorts <- read.csv(file = system.file("settings", "CohortsToCreate.csv", package = "Covid19SusceptibilityAlphaBlockers")) %>% select(cohortId, shinyName)

aceMonoId <- cohorts %>% filter(shinyName == "ACE mono") %>% select(cohortId) %>% pull()
arbMonoId <- cohorts %>% filter(shinyName == "ARB mono") %>% select(cohortId) %>% pull()
aceArbMonoId <- cohorts %>% filter(shinyName == "ACE/ARB mono") %>% select(cohortId) %>% pull()
ccbThzMonoId <- cohorts %>% filter(shinyName == "CCB/THZ mono") %>% select(cohortId) %>% pull()

aceComboId <- cohorts %>% filter(shinyName == "ACE +combo") %>% select(cohortId) %>% pull()
arbComboId <- cohorts %>% filter(shinyName == "ARB +combo") %>% select(cohortId) %>% pull()
aceArbComboId <- cohorts %>% filter(shinyName == "ACE/ARB +combo") %>% select(cohortId) %>% pull()
ccbThzComboId <- cohorts %>% filter(shinyName == "CCB/THZ +combo") %>% select(cohortId) %>% pull()

ccbMonoId <- cohorts %>% filter(shinyName == "CCB mono") %>% select(cohortId) %>% pull()
thzMonoId <- cohorts %>% filter(shinyName == "THZ mono") %>% select(cohortId) %>% pull()
ccbComboId <- cohorts %>% filter(shinyName == "CCB +combo") %>% select(cohortId) %>% pull()
thzComboId <- cohorts %>% filter(shinyName == "THZ +combo") %>% select(cohortId) %>% pull()

covidNarrowId <- cohorts %>% filter(shinyName == "COVID-19 diagnosis") %>% select(cohortId) %>% pull()
covidBroadId <- cohorts %>% filter(shinyName == "COVID-19 hospitalization") %>% select(cohortId) %>% pull()

pnaId <- cohorts %>% filter(shinyName == "Pneumonia") %>% select(cohortId) %>% pull()
adverseId <- cohorts %>% filter(shinyName == "PAAS event") %>% select(cohortId) %>% pull()

prettyNames <- data.frame(
  cohortId = c(aceMonoId, arbMonoId, aceArbMonoId, ccbMonoId, thzMonoId, ccbThzMonoId,
               aceComboId, arbComboId, aceArbComboId, ccbComboId, thzComboId, ccbThzComboId),
  cohortName = c("ACE", "ARB", "ACE/ARB", "CCB", "THZ", "CCB/THZ",
                 "ACE+", "ARB+", "ACE/ARB+", "CCB+", "THZ+", "CCB/THZ+"))

primaryAnalysisId <- 5 # Full stratified PS
```


\clearpage

# Sample sizes, total follow-up times and events

```{r, echo=FALSE, warning=FALSE, message=FALSE}

sidiapDir <- "/Users/msuchard/Dropbox/Projects/Covid19Icarius/SIDIAP"
cuimcDir <- "/Users/msuchard/Dropbox/Projects/Covid19Icarius/CUIMC"
vaDir <- "/Users/msuchard/Dropbox/Projects/Covid19Icarius/VA-OMOP"

studyFolder <- "/Users/msuchard/Dropbox/Projects/Covid19Icarius"

```

# Cohort balance and systematic error diagnostics

```{r, echo=FALSE}
plotScatter <- function(controlResults) {
  size <- 2
  labelY <- 1.5
  d <- rbind(data.frame(yGroup = "Uncalibrated",
                        logRr = controlResults$logRr,
                        seLogRr = controlResults$seLogRr,
                        ci95Lb = controlResults$ci95Lb,
                        ci95Ub = controlResults$ci95Ub,
                        trueRr = controlResults$effectSize),
             data.frame(yGroup = "Calibrated",
                        logRr = controlResults$calibratedLogRr,
                        seLogRr = controlResults$calibratedSeLogRr,
                        ci95Lb = controlResults$calibratedCi95Lb,
                        ci95Ub = controlResults$calibratedCi95Ub,
                        trueRr = controlResults$effectSize))
  d <- d[!is.na(d$logRr), ]
  d <- d[!is.na(d$ci95Lb), ]
  d <- d[!is.na(d$ci95Ub), ]
  if (nrow(d) == 0) {
    return(NULL)
  }
  d$Group <- as.factor(d$trueRr)
  d$Significant <- d$ci95Lb > d$trueRr | d$ci95Ub < d$trueRr
  temp1 <- aggregate(Significant ~ Group + yGroup, data = d, length)
  temp2 <- aggregate(Significant ~ Group + yGroup, data = d, mean)
  temp1$nLabel <- paste0(formatC(temp1$Significant, big.mark = ","), " estimates")
  temp1$Significant <- NULL

  temp2$meanLabel <- paste0(formatC(100 * (1 - temp2$Significant), digits = 1, format = "f"),
                            "% of CIs include ",
                            temp2$Group)
  temp2$Significant <- NULL
  dd <- merge(temp1, temp2)
  dd$tes <- as.numeric(as.character(dd$Group))

  breaks <- c(0.1, 0.25, 0.5, 1, 2, 4, 6, 8, 10)
  theme <- ggplot2::element_text(colour = "#000000", size = 12)
  themeRA <- ggplot2::element_text(colour = "#000000", size = 12, hjust = 1)
  themeLA <- ggplot2::element_text(colour = "#000000", size = 12, hjust = 0)

  d$Group <- paste("True hazard ratio =", d$Group)
  dd$Group <- paste("True hazard ratio =", dd$Group)
  alpha <- 1 - min(0.95 * (nrow(d)/nrow(dd)/50000)^0.1, 0.95)
  plot <- ggplot2::ggplot(d, ggplot2::aes(x = logRr, y = seLogRr), environment = environment()) +
          ggplot2::geom_vline(xintercept = log(breaks), colour = "#AAAAAA", lty = 1, size = 0.5) +
          ggplot2::geom_abline(ggplot2::aes(intercept = (-log(tes))/qnorm(0.025), slope = 1/qnorm(0.025)),
                               colour = rgb(0.8, 0, 0),
                               linetype = "dashed",
                               size = 1,
                               alpha = 0.5,
                               data = dd) +
          ggplot2::geom_abline(ggplot2::aes(intercept = (-log(tes))/qnorm(0.975), slope = 1/qnorm(0.975)),
                               colour = rgb(0.8, 0, 0),
                               linetype = "dashed",
                               size = 1,
                               alpha = 0.5,
                               data = dd) +
          ggplot2::geom_point(size = size,
                              color = rgb(0, 0, 0, alpha = 0.05),
                              alpha = alpha,
                              shape = 16) +
          ggplot2::geom_hline(yintercept = 0) +
          ggplot2::geom_label(x = log(0.15),
                              y = 1.9,
                              alpha = 1,
                              hjust = "left",
                              ggplot2::aes(label = nLabel),
                              size = 3,
                              data = dd) +
          ggplot2::geom_label(x = log(0.15),
                              y = labelY,
                              alpha = 1,
                              hjust = "left",
                              ggplot2::aes(label = meanLabel),
                              size = 3,
                              data = dd) +
          ggplot2::scale_x_continuous("Hazard ratio",
                                      limits = log(c(0.1, 10)),
                                      breaks = log(breaks),
                                      labels = breaks) +
          ggplot2::scale_y_continuous("Standard Error", limits = c(0, 2)) +
          ggplot2::facet_grid(yGroup ~ Group) +
          ggplot2::theme(panel.grid.minor = ggplot2::element_blank(),
                         panel.background = ggplot2::element_blank(),
                         panel.grid.major = ggplot2::element_blank(),
                         axis.ticks = ggplot2::element_blank(),
                         axis.text.y = themeRA,
                         axis.text.x = theme,
                         axis.title = theme,
                         legend.key = ggplot2::element_blank(),
                         strip.text.x = theme,
                         strip.text.y = theme,
                         strip.background = ggplot2::element_blank(),
                         legend.position = "none")

  return(plot)
}

getAllControls <- function() {
  pathToCsv <- system.file("settings", "NegativeControls.csv", package = "Covid19SusceptibilityAlphaBlockers")
  allControls <- read.csv(pathToCsv)
  allControls$oldOutcomeId <- allControls$outcomeId
  allControls$targetEffectSize <- rep(1, nrow(allControls))
  return(allControls)
}

getControlResults <- function(tId, cId, aId, dId, negativeControlOutcomeIds, results) {
  results <- results %>% filter(targetId == tId, comparatorId == cId, 
                                analysisId == aId, databaseId == dId, 
                                outcomeId %in% negativeControlOutcomeIds) %>%
    mutate(effectSize = 1)
  return(results)
}

negativeControlOutcomeIds <- unique(getAllControls()$outcomeId)
```


```{r, echo=FALSE}
plotCovariateBalanceScatterPlot <- function(balance, beforeLabel = "Before stratification", afterLabel = "After stratification") {
  limits <- c(min(c(balance$absBeforeMatchingStdDiff, balance$absAfterMatchingStdDiff),
                  na.rm = TRUE),
              max(c(balance$absBeforeMatchingStdDiff, balance$absAfterMatchingStdDiff),
                  na.rm = TRUE))
  theme <- ggplot2::element_text(colour = "#000000", size = 12)
  plot <- ggplot2::ggplot(balance, ggplot2::aes(x = absBeforeMatchingStdDiff, y = absAfterMatchingStdDiff)) +
    ggplot2::geom_point(color = rgb(0, 0, 0.8, alpha = 0.3), shape = 16, size = 2) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::geom_hline(yintercept = 0) +
    ggplot2::geom_vline(xintercept = 0) +
    ggplot2::scale_x_continuous(beforeLabel, limits = limits) +
    ggplot2::scale_y_continuous(afterLabel, limits = limits) +
    ggplot2::theme(text = theme)
  
  return(plot)
}

getPs <- function(dataFolder, targetIds, comparatorIds, analysisId, databaseId) {
  file <- sprintf("preference_score_dist_t%s_c%s_%s.rds", targetIds, comparatorIds, databaseId)
  ps <- readRDS(file.path(dataFolder, file))
  colnames(ps) <- SqlRender::snakeCaseToCamelCase(colnames(ps))
  ps <- ps[ps$analysisId == analysisId, ]
  return(ps)
}

plotPs <- function(ps, targetName, comparatorName) {
  ps <- rbind(data.frame(x = ps$preferenceScore, y = ps$targetDensity, group = targetName),
              data.frame(x = ps$preferenceScore, y = ps$comparatorDensity, group = comparatorName))
  ps$group <- factor(ps$group, levels = c(as.character(targetName), as.character(comparatorName)))
  theme <- ggplot2::element_text(colour = "#000000", size = 12, margin = ggplot2::margin(0, 0.5, 0, 0.1, "cm"))
  plot <- ggplot2::ggplot(ps,
                          ggplot2::aes(x = x, y = y, color = group, group = group, fill = group)) +
          ggplot2::geom_density(stat = "identity") +
          ggplot2::scale_fill_manual(values = c(rgb(0.8, 0, 0, alpha = 0.5),
                                                rgb(0, 0, 0.8, alpha = 0.5))) +
          ggplot2::scale_color_manual(values = c(rgb(0.8, 0, 0, alpha = 0.5),
                                                 rgb(0, 0, 0.8, alpha = 0.5))) +
          ggplot2::scale_x_continuous("Preference score", limits = c(0, 1)) +
          ggplot2::scale_y_continuous("Density") +
          ggplot2::theme(legend.title = ggplot2::element_blank(),
                         panel.grid.major = ggplot2::element_blank(),
                         panel.grid.minor = ggplot2::element_blank(),
                         legend.position = "top",
                         legend.text = theme,
                         axis.text = theme,
                         axis.title = theme)
  return(plot)
}

makeSideBySideBalancePlots <- function(databaseId, covariate, cmResults,
                                       targetId, comparatorId,
                                       thisOutcomeId,
                                       studyFolder) {

  balanceStrat <- getCovariateBalance(NULL, targetId, comparatorId, 
                                      databaseId = databaseId, analysisId = primaryAnalysisId,
                                      outcomeId = thisOutcomeId,
                                      covariate = covariate, 
                                      dataFolder = file.path(studyFolder, 
                                                             databaseId, "shinyData"))
  
  plotStrat <- plotCovariateBalanceScatterPlot(balanceStrat,
                                               beforeLabel = "Before stratification", 
                                               afterLabel = "After stratification")
  
  balanceMatch <- getCovariateBalance(NULL, targetId, comparatorId, 
                                      databaseId = databaseId, analysisId = 6,
                                      outcomeId = thisOutcomeId,
                                      covariate = covariate, 
                                      dataFolder = file.path(studyFolder, 
                                                             databaseId, "shinyData"))
  
  plotMatch <- plotCovariateBalanceScatterPlot(balanceMatch,
                                               beforeLabel = "Before matching", 
                                               afterLabel = "After matching")
  
  psStrat <- getPs(file.path(studyFolder, databaseId, "shinyData"), targetId, comparatorId, primaryAnalysisId, databaseId)
  
  targetName <- cohorts %>% filter(cohortId == targetId) %>% select(shinyName) %>% pull()
  comparatorName <- cohorts %>% filter(cohortId == comparatorId) %>% select(shinyName) %>% pull()

  psStrat <- plotPs(psStrat, targetName, comparatorName)  
  
  # psMatch <- getPs(file.path(studyFolder, databaseId, "shinyData"), targetId, comparatorId, 6, databaseId)
  # 
  # psMatch <- plotPs(psMatch, 
  #                   cohorts %>% filter(cohortId == targetId) %>% select(shinyName) %>% pull(),
  #                   cohorts %>% filter(cohortId == comparatorId) %>% select(shinyName) %>% pull())   
  
controlsStrat <- getControlResults(targetId, comparatorId, 5, databaseId, negativeControlOutcomeIds,
                                   cmResults)

controlsMatch <- getControlResults(targetId, comparatorId, 6, databaseId, negativeControlOutcomeIds,
                                   cmResults)

errorStrat <- plotScatter(controlsStrat)
errorMatch <- plotScatter(controlsMatch)
  
  return(list(plotStrat = plotStrat, plotMatch  = plotMatch,
              psStrat = psStrat, 
              # psMatch = psMatch,
              balanceStrat = balanceStrat, balanceMatch = balanceMatch,
              errorStrat = errorStrat, errorMatch = errorMatch,
              targetId = targetId, comparatorId = comparatorId, 
              targetName = targetName, comparatorName = comparatorName,
              outcomeId = thisOutcomeId,
              databaseId = databaseId))
}

saveSideBySidePlots <- function(plot) {
  file <- sprintf("sideBySide_%d_%d_%d_%s.pdf", plot$targetId, plot$comparatorId, plot$outcomeId, 
                  plot$databaseId)
  invisible(save_plot(file,
            plot_grid(
              plot$psStrat, plot$plotStrat, plot$plotMatch, NULL, plot$errorStrat, plot$errorMatch, 
              ncol = 3, rel_heights = c(1, 1)),
            #base_asp = 0.5, 
            #ncol = 5,
            base_height = 8))
  return(list(file = file, targetName = plot$targetName,
              comparatorName = plot$comparatorName,
              databaseName = plot$databaseId))
}

makeExtremeBalanceTable <- function(balance,
                                    targetName, comparatorName, databaseId, designName,
                                    length) {
  originalNrow <- nrow(balance)
  
  balance <- balance %>% 
    arrange(-absAfterMatchingStdDiff) %>% head(length) %>%
    select(-covariateId, -analysisId, -absBeforeMatchingStdDiff, -absAfterMatchingStdDiff) %>%
    mutate(beforeMatchingMeanTreated = sprintf("%2.1f", beforeMatchingMeanTreated * 100),
           beforeMatchingMeanComparator = sprintf("%2.1f", beforeMatchingMeanComparator * 100),
           afterMatchingMeanTreated = sprintf("%2.1f", afterMatchingMeanTreated * 100),
           afterMatchingMeanComparator = sprintf("%2.1f", afterMatchingMeanComparator * 100))
  
  header <- readr::read_file("TableBalanceTop.tex")
  header <- gsub(pattern = "CHARACTERISTIC", 
                 paste0("Characteristic (total count = ", originalNrow, ")"),
                 header)
  header <- gsub(pattern = "DESIGN", designName, header)
  header <- gsub(pattern = "DATASOURCE", databaseId, header)
  header <- gsub(pattern = "TARGET", targetName, header)
  header <- gsub(pattern = "COMPARATOR", comparatorName, header)
  
  cat(header)
  print(xtable(balance, format = "latex"),
        include.rownames = FALSE,
        include.colnames = FALSE,
        hline.after = NULL,
        only.contents = TRUE)
  footer <- readr::read_file("TableBalanceBottom.tex")
  cat(footer)
}
```

## SIDIAP

```{r, echo=FALSE, results="asis", warning=FALSE, message=FALSE, cache=TRUE}

sidiapCovariate <- readRDS(file.path(studyFolder, "SIDIAP", "shinyData", paste0("covariate_", "SIDIAP", ".rds")))
colnames(sidiapCovariate) <- SqlRender::snakeCaseToCamelCase(colnames(sidiapCovariate))

sidiapResults <- readRDS(file.path(studyFolder, "SIDIAP", "shinyData", paste0("cohort_method_result_", "SIDIAP", ".rds")))
colnames(sidiapResults) <- SqlRender::snakeCaseToCamelCase(colnames(sidiapResults))

devNull <- lapply(tcs, function(tc) {
  balance <- makeSideBySideBalancePlots("SIDIAP", sidiapCovariate, sidiapResults,
                               tc$targetId, tc$comparatorId, covidNarrowId,
                               studyFolder)
  
  invisible(info <- saveSideBySidePlots(balance))
  
  figure <- readr::read_file("BalanceFig.tex")
  figure <- sub(pattern = "TARGET", replacement = info$targetName, x = figure)
  figure <- sub(pattern = "COMPARATOR", replacement = info$comparatorName, x = figure)
  figure <- sub(pattern = "DATASOURCE", replacement = info$databaseName, x = figure)
  figure <- sub(pattern = "FILENAME", replacement = info$file, x = figure)
  cat(figure)
  
  makeExtremeBalanceTable(balance$balanceStrat, balance$targetName, balance$comparatorName, 
                          "SIDIAP", "stratification", length = 10)
  
  makeExtremeBalanceTable(balance$balanceMatch, balance$targetName, balance$comparatorName, 
                          "SIDIAP", "matching", length = 10)
  
  cat("\\clearpage")
  
})
```


\clearpage

## VA-OMOP

```{r, echo=FALSE, results="asis", warning=FALSE, message=FALSE, cache=TRUE}

vaCovariate <- readRDS(file.path(studyFolder, "VA-OMOP", "shinyData", paste0("covariate_", "VA-OMOP", ".rds")))
colnames(vaCovariate) <- SqlRender::snakeCaseToCamelCase(colnames(vaCovariate))

vaResults <- readRDS(file.path(studyFolder, "VA-OMOP", "shinyData", paste0("cohort_method_result_", "VA-OMOP", ".rds")))
colnames(vaResults) <- SqlRender::snakeCaseToCamelCase(colnames(vaResults))

devNull <- lapply(tcs, function(tc) {
  balance <- makeSideBySideBalancePlots("VA-OMOP", vaCovariate, vaResults,
                               tc$targetId, tc$comparatorId, covidNarrowId,
                               studyFolder)
  
  invisible(info <- saveSideBySidePlots(balance))
  
  figure <- readr::read_file("BalanceFig.tex")
  figure <- sub(pattern = "TARGET", replacement = info$targetName, x = figure)
  figure <- sub(pattern = "COMPARATOR", replacement = info$comparatorName, x = figure)
  figure <- sub(pattern = "DATASOURCE", replacement = info$databaseName, x = figure)
  figure <- sub(pattern = "FILENAME", replacement = info$file, x = figure)
  cat(figure)
  
  makeExtremeBalanceTable(balance$balanceStrat, balance$targetName, balance$comparatorName, 
                          "VA-OMOP", "stratification", length = 10)
  
  makeExtremeBalanceTable(balance$balanceMatch, balance$targetName, balance$comparatorName, 
                          "VA-OMOP", "matching", length = 10)
  
  cat("\\clearpage")  
})
```

\clearpage

## CUIMC

```{r, echo=FALSE, results="asis", warning=FALSE, message=FALSE, cache=TRUE}

cuimcCovariate <- readRDS(file.path(studyFolder, "CUIMC", "shinyData", paste0("covariate_", "CUIMC", ".rds")))
colnames(cuimcCovariate) <- SqlRender::snakeCaseToCamelCase(colnames(cuimcCovariate))

cuimcResults <- readRDS(file.path(studyFolder, "CUIMC", "shinyData", paste0("cohort_method_result_", "CUIMC", ".rds")))
colnames(cuimcResults) <- SqlRender::snakeCaseToCamelCase(colnames(cuimcResults))

devNull <- lapply(tcs, function(tc) {
  balance <- makeSideBySideBalancePlots("CUIMC", cuimcCovariate, cuimcResults,
                               tc$targetId, tc$comparatorId, covidNarrowId,
                               studyFolder)
  
  invisible(info <- saveSideBySidePlots(balance))
  
  figure <- readr::read_file("BalanceFig.tex")
  figure <- sub(pattern = "TARGET", replacement = info$targetName, x = figure)
  figure <- sub(pattern = "COMPARATOR", replacement = info$comparatorName, x = figure)
  figure <- sub(pattern = "DATASOURCE", replacement = info$databaseName, x = figure)
  figure <- sub(pattern = "FILENAME", replacement = info$file, x = figure)
  cat(figure)
  
  makeExtremeBalanceTable(balance$balanceStrat, balance$targetName, balance$comparatorName, 
                          "CUIMC", "stratification", length = 10)
  
  makeExtremeBalanceTable(balance$balanceMatch, balance$targetName, balance$comparatorName, 
                          "CUIMC", "matching", length = 10)
  
  cat("\\clearpage")  
})
```
