---
params:
    save: NULL #"first.Rda"
    load: "first.Rda"
    completeReload: false
# bibliography: CohortDefinition.bib
# csl: nature-publishing-group-vancouver.csl
output:
  pdf_document:
    keep_tex: true
    md_extensions: +raw_attribute
    latex_engine: xelatex
mainfont: Arial
    #citation_package: natbib
    #rticles::sim_article
fontsize: 10pt
geometry: margin=1in
classoption: doublespace, table
longtable: true
header-includes:
  - \usepackage[numbers,sort&compress]{natbib}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{caption}
  - \usepackage{rotating}
  - \usepackage{multirow}
  - \usepackage{mwe,tikz}
  - \usepackage[percent]{overpic}
  - \usepackage{enumitem}
  - \usepackage{mas_fun}
  - \usepackage{hyperref}
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage[table]{xcolor}', x, fixed = TRUE)})
library(dplyr)
library(tidyr)
library(xtable)

readRdsCamelCase <- function(file) {
  result <- readRDS(file)
  colnames(result) <- SqlRender::snakeCaseToCamelCase(colnames(result))
  return(result)
}
```

\centerline{{\Huge Results: Incidence}}

<!-- \captionsetup[table]{name=Supplementary Table} -->
<!-- \captionsetup[figure]{name=Supplementary Figure} -->
\captionsetup{labelfont=bf}

# Cohorts

```{r, echo=FALSE}
cohorts <- read.csv(file = system.file("settings", "CohortsToCreate.csv", package = "Covid19SusceptibilityAlphaBlockers")) %>% select(cohortId, shinyName)

alphaBlockerId <- cohorts %>% filter(shinyName == "Alpha-1 blocker") %>% select(cohortId) %>% pull()
fiveAlphaId <- cohorts %>% filter(shinyName == "5ARI / PDE5") %>% select(cohortId) %>% pull()

covidNarrowId <- cohorts %>% filter(shinyName == "Diagnosis") %>% select(cohortId) %>% pull()
hospitalizationId <- cohorts %>% filter(shinyName == "Hospitalization") %>% select(cohortId) %>% pull()
intensiveServiceId <- cohorts %>% filter(shinyName == "Intensive services") %>% select(cohortId) %>% pull()

prettyNames <- data.frame(
  cohortId = c(alphaBlockerId, fiveAlphaId),
  cohortName = c("Alpha-1 blocker", "5ARI / PDE5"))

analysisIdToKeep <- c(5, 6)
primaryAnalysisId <- 5 # Full stratified PS
```


# Sample sizes

```{r, echo=FALSE, warning=FALSE, message=FALSE}

studyFolder <- "/Users/aki-nishimura/Dropbox/Documents_Academic/Covid19AlphaBlocker"
databaseIds <- c("SIDIAP", "VA-OMOP", "CUIMC")
dataDirs <- sapply(databaseIds, function (databaseId) file.path(studyFolder, databaseId))

makeSampleSizeTable <- function(databaseId, 
                                dataFolder,
                                databaseOrder = 1) {
  cmResults <- readRDS(file = file.path(dataFolder, paste0("cohort_method_result_", databaseId, ".rds")))
  colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
  alpha <- 0.05
  power <- 0.8
  z1MinAlpha <- qnorm(1 - alpha/2)
  zBeta <- -qnorm(1 - power)
  pA <- cmResults$targetSubjects/(cmResults$targetSubjects + cmResults$comparatorSubjects)
  pB <- 1 - pA
  totalEvents <- abs(cmResults$targetOutcomes) + (cmResults$comparatorOutcomes)
  cmResults$mdrr <- exp(sqrt((zBeta + z1MinAlpha)^2/(totalEvents * pA * pB)))
  cmResults$targetYears <- cmResults$targetDays/365.25
  cmResults$comparatorYears <- cmResults$comparatorDays/365.25
  
  cmResults <- cmResults %>% filter(analysisId %in% analysisIdToKeep, outcomeId == covidNarrowId)
  
  table <- rbind(
    cmResults %>% filter(targetId == alphaBlockerId, comparatorId == fiveAlphaId) %>% mutate(targetId = "Alpha-1 blocker", comparatorId = "5ARI / PDE5", order = 1)
  ) %>% mutate (databaseId = databaseId, databaseOrder = databaseOrder) %>% 
    select(targetId, comparatorId, databaseId, targetSubjects, comparatorSubjects, targetYears, comparatorYears, targetOutcomes, comparatorOutcomes, mdrr, order, databaseOrder)
  
  table$targetSubjects <- formatC(table$targetSubjects, big.mark = ",", format = "d")
  table$comparatorSubjects <- formatC(table$comparatorSubjects, big.mark = ",", format = "d")
  table$targetYears <- formatC(table$targetYears, big.mark = ",", format = "d")
  table$comparatorYears <- formatC(table$comparatorYears, big.mark = ",", format = "d")
  table$targetOutcomes <- formatC(table$targetOutcomes, big.mark = ",", format = "d")
  table$comparatorOutcomes <- formatC(table$comparatorOutcomes, big.mark = ",", format = "d")
  # table$targetIr <- sprintf("%.2f", table$targetIr)
  # table$comparatorIr <- sprintf("%.2f", table$comparatorIr)
  table$mdrr <- sprintf("%.2f", table$mdrr)
  table$targetSubjects <- gsub("^-", "<", table$targetSubjects)
  table$comparatorSubjects <- gsub("^-", "<", table$comparatorSubjects)
  table$targetOutcomes <- gsub("^-", "<", table$targetOutcomes)
  table$comparatorOutcomes <- gsub("^-", "<", table$comparatorOutcomes)
  # table$targetIr <- gsub("^-", "<", table$targetIr)
  # table$comparatorIr <- gsub("^-", "<", table$comparatorIr)
  return(table)
}

tables <- lapply(
  1:length(databaseIds),
  function (i) makeSampleSizeTable(
    databaseId = databaseIds[i], 
    dataFolder = file.path(dataDirs[i], "shinyData"), 
    databaseOrder = i
  ) 
)
names(tables) <- databaseIds

table <- bind_rows(tables) %>% arrange(order, databaseOrder) %>% 
  mutate(targetId = "", comparatorId = "") %>% select(-order, -databaseOrder)
```

\begin{table}[H]
 \caption{Population size, total exposure time and COVID-19 diagnoses for ACEI, ARB and CCB/THZ monotherapy and in-combination user target (T) and comparator (C) cohorts.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}rrrrrrrr}
    \hiderowcolors
    \toprule
    &  &  & \multicolumn{2}{c}{Patients} & \multicolumn{2}{c}{Time (years)} & \multicolumn{2}{c}{Events} \\
    \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
    &  &
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C} 
    & MDRR \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(table, format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      add.to.row = list(
        pos = as.list(c(0) * 3),
        command = c(
          "                       \\multicolumn{9}{l}{Alpha-1 blocker vs 5ARI / PDE5} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\"
          # "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ACE vs ARB} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{8}{l}{+ Combination} \\\\"
          )
      ),
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}   

```{r, echo=FALSE}
countText <- function(targetName = "ACE/ARB (c)",
                      comparatorName = "CCB/THZ (c)") {
  
  tS <- do.call("rbind",
                lapply(tables, function(tab) {
                  tab %>% filter(targetId == targetName, comparatorId == comparatorName) %>%
                    mutate(targetSubjects = as.numeric(sub(",", "", targetSubjects)),
                           comparatorSubjects = as.numeric(sub(",", "", comparatorSubjects)),
                           targetYears = as.numeric(sub(",", "", targetYears)),
                           comparatorYears = as.numeric(sub(",", "", comparatorYears)),
                           targetOutcomes = as.numeric(sub(",", "", targetOutcomes)),
                           comparatorOutcomes = as.numeric(sub(",", "", comparatorOutcomes))
                    )
                }))
  
  cat(sum(tS$targetSubjects), "\n")
  cat(sum(tS$comparatorSubjects), "\n")
  cat("\n")
  cat(sum(tS$targetYears), "\n")
  cat(sum(tS$comparatorYears), "\n")
  cat("\n")
  cat(sum(tS$targetOutcomes) / sum(tS$targetYears) * 1000, "\n")
  cat(sum(tS$comparatorOutcomes) / sum(tS$comparatorYears) * 1000, "\n")
}
```

```{r, echo=TRUE}
countText(targetName = "Alpha-1 blocker", comparatorName = "5ARI / PDE5")
```

```{r, echo=FALSE}
source(system.file("shiny", "EvidenceExplorer", "PlotsAndTables.R",
                   package = "Covid19SusceptibilityAlphaBlockers"))
```

```{r, echo=FALSE, results="asis", cache=FALSE, warning=FALSE}

getCovariateBalance <- function(connection,
                                targetId,
                                comparatorId,
                                databaseId,
                                analysisId,
                                covariate,
                                dataFolder,
                                outcomeId = NULL) {
  file <- sprintf("covariate_balance_t%s_c%s_%s.rds", targetId, comparatorId, databaseId)
  balance <- readRDS(file.path(dataFolder, file))
  colnames(balance) <- SqlRender::snakeCaseToCamelCase(colnames(balance))
  balance <- balance[balance$analysisId == analysisId & balance$outcomeId == outcomeId, ]
  balance <- merge(balance, covariate[covariate$databaseId == databaseId & covariate$analysisId == analysisId, 
                                      c("covariateId", "covariateAnalysisId", "covariateName")])
  balance <- balance[ c("covariateId",
                        "covariateName",
                        "covariateAnalysisId", 
                        "targetMeanBefore", 
                        "comparatorMeanBefore", 
                        "stdDiffBefore", 
                        "targetMeanAfter", 
                        "comparatorMeanAfter",
                        "stdDiffAfter")]
  colnames(balance) <- c("covariateId",
                         "covariateName",
                         "analysisId",
                         "beforeMatchingMeanTreated",
                         "beforeMatchingMeanComparator",
                         "beforeMatchingStdDiff",
                         "afterMatchingMeanTreated",
                         "afterMatchingMeanComparator",
                         "afterMatchingStdDiff")
  balance$absBeforeMatchingStdDiff <- abs(balance$beforeMatchingStdDiff)
  balance$absAfterMatchingStdDiff <- abs(balance$afterMatchingStdDiff)
  return(balance)
}

blend <- function(databaseIds,
                  targetId,
                  comparatorId,
                  dataFolders,
                  outcomeId = covidNarrowId) {
  
  harmonizeRace <- function(table) {
    
    aggregate <- function(x) {
      sprintf(" %2.1f", sum(as.numeric(x), na.rm = TRUE))
    }
    
    # Combine Asians
    combinedAsian <- c("    race = Asian", "    race = Asian Indian", "    race = Chinese", 
                       "    race = Filipino", "    race = Korean", "    race = Laotian", "    race = Vietnamese")
    asian <- table %>% filter(id %in% combinedAsian)
    b <- aggregate(asian$b)
    c <- aggregate(asian$c)
    e <- aggregate(asian$e)
    f <- aggregate(asian$f)
    
    asianKeep <- table$id == "    race = Asian"
    table$b[asianKeep] <- b
    table$c[asianKeep] <- c
    table$e[asianKeep] <- e
    table$f[asianKeep] <- f
    
    table <- table %>% filter(!(id %in% combinedAsian[-1]))
    
    # Recode Pacific Islander
    table$id <- as.character(table$id)
    table$id[table$id == "    race = Other Pacific Islander"] <- "    race = Native Hawaiian or Other Pacific Islander"
    
    # Combine other and unknown
    combinedMisc <- c("    race = Unknown", "    race = Other Race")
    misc <- table %>% filter(id %in% combinedMisc)
    b <- aggregate(misc$b)
    c <- aggregate(misc$c)
    e <- aggregate(misc$e)
    f <- aggregate(misc$f)
    
    miscKeep <- table$id == "    race = Unknown"
    table$b[miscKeep] <- b
    table$c[miscKeep] <- c
    table$e[miscKeep] <- e
    table$f[miscKeep] <- f
    
    table <- table %>% filter(!(id %in% combinedMisc[-1]))
    
    # Remove first native Hawaiian
    index <- table$id == "    race = Native Hawaiian or Other Pacific Islander"
    if (sum(index) > 1) {
      index[which(index)[2]] <- FALSE
      table <- table[!index, ]
    }
    
    return(table)
  }
                     
  createTable <- function (balance, dataFolder, databaseId) {
    
    covariate <- readRDS(file.path(dataFolder, paste0("covariate_", databaseId, ".rds")))
    colnames(covariate) <- SqlRender::snakeCaseToCamelCase(colnames(covariate))
    balance <- getCovariateBalance(
      NULL, targetId, comparatorId, databaseId = databaseId, analysisId = primaryAnalysisId,
      outcomeId = outcomeId, covariate = covariate, dataFolder = dataFolder
    )
    # prepareTable1() is from PlotsAndTables.R under EvidenceExplorer
    pathToCsv <- system.file("shiny", "EvidenceExplorer", "Table1Specs.csv", package = "Covid19SusceptibilityAlphaBlockers")
    table <- prepareTable1(balance, pathToCsv = pathToCsv)

    table <- table[3:nrow(table), ]
    colnames(table) <- c("id","b","c","d","e","f","g")
    table <- harmonizeRace(table)
    table$order <- c(1:nrow(table))
    
    return(table)
  }
  
  balances <- lapply(1:length(databaseIds), 
    function (i) {
      covariate <- readRDS(file.path(dataFolders[i], paste0("covariate_", databaseIds[i], ".rds")))
      colnames(covariate) <- SqlRender::snakeCaseToCamelCase(colnames(covariate))
      balance <- getCovariateBalance(
        NULL, targetId, comparatorId, databaseId = databaseIds[i], analysisId = primaryAnalysisId,
        outcomeId = outcomeId, covariate = covariate, dataFolder = dataFolders[i]
      )
    }
  )
  numCovariates <- sapply(balances, nrow)
  tables <- lapply(1:length(databaseIds),
    function (i) { createTable(balances[[i]], dataFolders[i], databaseIds[i])  }
  )
  specifications <- read.csv(system.file("shiny", "EvidenceExplorer", "Table1Specs.csv",
                                      package = "Covid19SusceptibilityAlphaBlockers"), stringsAsFactors = FALSE)

  return(list(tables = tables, specifications = specifications, numCovariates = numCovariates))
}

tmp <- blend(alphaBlockerId, fiveAlphaId,
             databaseIds = databaseIds,
             dataFolders = sapply(dataDirs, function (dataDir) file.path(dataDir, "shinyData")))
 
numCovariates <- tmp$numCovariates
names(numCovariates) <- databaseIds

table_tmp <- tmp$tables[[1]]
for (i in 2:length(databaseIds)) {
  table_tmp <- full_join(table_tmp, tmp$tables[[i]], 
                         by = 'id', suffix = c(sprintf(".%d", i - 1), sprintf(".%d", i)))
}
if (length(databaseIds) == 3) {
  # Not sure why this is necessary only for length(databaseIds) == 3
  table_tmp <- table_tmp %>%
    rename(b.3 = b, c.3 = c, d.3 = d, e.3 = e, f.3 = f, g.3 = g, order.3 = order)
}
 
tableOrder <- read.csv("CombinedDemographics.csv")
t3 <- full_join(table_tmp, tableOrder, by = "id") %>% arrange(order) %>% 
  filter(order < 300) %>%
  mutate(id = newNames) %>%
  select(-starts_with("order"), -newNames)
t3[is.na(t3)] <- ""
t3$id <- sub("    ", "\\\\hspace{1em} ", as.character(t3$id))

targetId <- alphaBlockerId
comparatorId <- fiveAlphaId
databaseId = "SIDIAP, VA and CUIMC" 

# Get counts for header
tcs <- lapply(
  tables, function (table) table %>% head(1) %>% select(targetSubjects, comparatorSubjects)
)

  scale <- 0.8
  header <- readr::read_file("Table1TopTriple.tex")

  targetName <- cohorts %>% filter(cohortId == targetId) %>% select(shinyName) %>% pull
  comparatorName <- cohorts %>% filter(cohortId == comparatorId) %>% select(shinyName) %>% pull
  title <- sub(pattern = "Patient demographics",
               replacement = paste0("Baseline patient characteristcs for ", targetName," (T) and ", comparatorName, " (C) prevalent-users in the ", databaseId, " data source"),
               x = header)

  title <- sub("0.5\\\\textwidth", paste0(scale, "\\\\textwidth"), x = title)
  title <- sub("-0.5em", "+0.5em", x = title)

  title <- gsub("% Extra row",
              paste(
                c(
                  sapply(databaseIds,
                    function (databaseId) {
                      paste0("& \\\\multicolumn{3}{c}{$N$ = ", tcs[[databaseId]]$targetSubjects, 
                        " } & \\\\multicolumn{3}{c}{$N$ = ", tcs[[databaseId]]$comparatorSubjects, " } ")
                    }
                  ), 
                  " \\\\\\\\"
                ), 
                collapse = ""
              ),
               # , "\\\\\\\\ \n",
               #        "\& \\\\multicolumn{3}{c}{Before stratification} \& \\\\multicolumn{3}{c}{After stratification} "),
              x = title)
  
  # if (targetName == "THZ" && comparatorName == "ARB") {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat*", title)
  # } else {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat", title)
  # }

  cat(title)
  
  table <- t3 # %>% select(-order.y, -order)

  print(xtable(table, format = "latex", align = c("l", "l", rep("r", 6 * length(databaseIds)))),
        include.rownames = FALSE,
        include.colnames = FALSE,
        hline.after = NULL,
        only.contents = TRUE,
        add.to.row = list(pos = list(nrow(table)), command = c("\\bottomrule")),
        sanitize.text.function = identity)

  footer <- readr::read_file("Table1BottomTriple.tex")
  cat(footer)

```

## Numbers of covariates

```{r}
numCovariates
```

```{r, echo=FALSE, cache=FALSE}

tcs <- list(
  list(alphaBlockerId, fiveAlphaId)
)
tcs <- lapply(tcs, function(x) { names(x) <- c("targetId", "comparatorId"); return(x) })

outcomesOfInterest <- c(972, 974, 981)

processCmResults <- function (databaseId) {
  cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
  colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
  cmResults <- cmResults %>% filter(outcomeId %in% outcomesOfInterest, analysisId %in% c(5,6))
  return(cmResults)
}

databaseId <- "Meta-analysis"
cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
cmResultsMa <- cmResults %>% filter(outcomeId %in% outcomesOfInterest, analysisId %in% c(5,6))
cmResultsMaWithSources <- cmResultsMa
cmResultsMa <- cmResultsMa %>% select(-sources)

cmResultsList <- lapply(c(databaseIds, "Meta-analysis"), processCmResults)
names(cmResultsList) <- c(databaseIds, "Meta-analysis")
cmResultsMaWithSources <- cmResultsList[["Meta-analysis"]]
cmResultsList[["Meta-analysis"]] <- cmResultsMaWithSources %>% select(-sources)
cmResults <- bind_rows(cmResultsList)

table <- do.call(
  "rbind",
  lapply(tcs, function(tc) {
    out <- cmResults %>% filter(targetId == tc$targetId, comparatorId == tc$comparatorId) %>%
      mutate(ci = ifelse(ci95Ub > 10,
                         sprintf("(%1.2f - %2.1f)", ci95Lb, ci95Ub),
                         sprintf("(%1.2f - %1.2f)", ci95Lb, ci95Ub)), 
             calibratedCi = ifelse(calibratedCi95Ub > 10,
                         sprintf("(%1.2f - %2.1f)", calibratedCi95Lb, calibratedCi95Ub),
                         sprintf("(%1.2f - %1.2f)", calibratedCi95Lb, calibratedCi95Ub))) %>% 
               # 
               # 
               # sprintf("(%1.2f - %1.2f)", calibratedCi95Lb, calibratedCi95Ub)) %>%
      select(databaseId, targetId, comparatorId, outcomeId, analysisId,
             calibratedRr, calibratedCi, calibratedP, calibratedCi95Lb, calibratedCi95Ub, i2) %>%
      left_join(prettyNames, by = c("targetId" = "cohortId")) %>% rename(targetName = cohortName) %>%
      left_join(prettyNames, by = c("comparatorId" = "cohortId")) %>% rename(comparatorName = cohortName) %>%
      select(-targetId, -comparatorId) %>%
      select(targetName, comparatorName, everything())
    return(out)
  }))
```

```{r, echo=FALSE, cache=FALSE}

covariates <- lapply(
  databaseIds, 
  function (databaseId) readRdsCamelCase(
    file.path(dataDirs[[databaseId]], "shinyData", sprintf("covariate_%s.rds", databaseId))
  )
)
names(covariates) <- databaseIds

getBalanceDiagnostic <- function(targetId, comparatorId, databaseId, analysisId, outcomeId, covariate, dataFolder) {
  balance <- getCovariateBalance(NULL, 
                                 targetId, comparatorId, 
                                 databaseId = databaseId, analysisId = analysisId, 
                                 outcomeId = outcomeId, 
                                 covariate = covariate, dataFolder = dataFolder)
  data.frame(databaseId = databaseId, analysisId = analysisId,
             targetId = targetId, comparatorId = comparatorId,
             imbalanced = sum(balance$absAfterMatchingStdDiff > 0.1, na.rm = TRUE))
}

analysisIds <- c(5, 6)
rbindBalanceDiagnosticOverAnalysisAndTcs <- function (databaseId) {
  bind_rows(
    lapply(analysisIds, 
      function (analysisId) {
        bind_rows(
          lapply(tcs, 
          function(tc) {
            getBalanceDiagnostic(
              tc$targetId, tc$comparatorId, databaseId, analysisId, covidNarrowId,
              covariates[[databaseId]], file.path(dataDirs[[databaseId]], "shinyData")
            )}
          )
        )
      }
    )
  )
}

balance <- bind_rows(
    lapply(databaseIds, rbindBalanceDiagnosticOverAnalysisAndTcs)
  ) %>% 
  left_join(prettyNames, by = c("targetId" = "cohortId")) %>% rename(targetName = cohortName) %>%
  left_join(prettyNames, by = c("comparatorId" = "cohortId")) %>% rename(comparatorName = cohortName) %>%
  select(-targetId, -comparatorId) %>%
  select(targetName, comparatorName, everything())  

  # Add meta-analysis
  meta <- table %>% filter(databaseId == "Meta-analysis", outcomeId == covidNarrowId) %>% 
    mutate(imbalanced = i2 > 0.40) %>%
    select(targetName, comparatorName, databaseId, analysisId, imbalanced)
  balance <- rbind(balance, meta) # Comment out to remove meta-analysis

table <- inner_join(table, balance, by = c("targetName", "comparatorName", "databaseId", "analysisId"))
```

# Info about meta-analysis

```{r, echo=FALSE}
meta <- cmResultsMaWithSources %>%
  left_join(prettyNames, by = c("targetId" = "cohortId")) %>% rename(targetName = cohortName) %>%
  left_join(prettyNames, by = c("comparatorId" = "cohortId")) %>% rename(comparatorName = cohortName) %>%
  select(-targetId, -comparatorId) %>%
  select(targetName, comparatorName, everything())   

knitr::kable(meta %>% filter(outcomeId == covidNarrowId, databaseId == "Meta-analysis") %>%
               arrange(analysisId) %>%
               filter(!is.na(is)) %>% select(targetName, comparatorName, analysisId, databaseId, i2, sources), 
             format = "latex",
             booktabs = TRUE)

table <- table %>% select(-i2) %>% 
  mutate(databaseId = ifelse(databaseId == "Meta-analysis", "Meta-analysis", databaseId))

```


```{r, echo=FALSE}
table5 <- table %>% filter(analysisId == 5) %>% select(-analysisId) %>%
  select(-calibratedCi95Lb, -calibratedCi95Ub) %>%
  rename(stratCalRr = calibratedRr, stratCalCi = calibratedCi, stratCalP = calibratedP, stratImbalanced = imbalanced)
table6 <- table %>% filter(analysisId == 6) %>% select(-analysisId) %>%
  select(-calibratedCi95Lb, -calibratedCi95Ub) %>%
  rename(matchCalRr = calibratedRr, matchCalCi = calibratedCi, matchCalP = calibratedP, matchImbalanced = imbalanced)
wideTable <- inner_join(table5, table6, by = c("databaseId", "targetName", "comparatorName", "outcomeId"))
```

\begin{table}[H]
 \caption{Relative risk of COVID-19 diagnosis for ACE inhibitors, ARB, CCB and THZ prevalent-users. We report calibrated hazard ratios (HRs) and their 95\% confidence intervals (CIs) across data sources.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}lrrr}
    \hiderowcolors
    \toprule
     & 
    & & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}

numDb <- length(unique(wideTable$databaseId))

print(xtable(wideTable %>% filter(outcomeId == covidNarrowId) %>% 
               #mutate(calibratedRr = ifself(is.na(calibratedRr), "--", calibratedRr)) %>%
               select(-outcomeId, -stratImbalanced, -matchCalRr, -matchCalCi, -matchCalP, -matchImbalanced) %>%
               mutate(targetName = "", comparatorName = ""), 
             format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
 add.to.row = list(
        pos = as.list(c(0) * numDb),
        command = c(
          "                       \\multicolumn{6}{l}{Alpha-1 blocker vs 5ARI / PDE5} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\"
          # "                        & \\multicolumn{5}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{6}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{5}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{6}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{5}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{6}{l}{ACE vs ARB} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{5}{l}{+ Combination} \\\\"          
          )
      ),      
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}

\definecolor{light-gray}{gray}{0.50}
\begin{table}[H]
 \caption{Relative risk of COVID-19 diagnosis for ACE inhibitors, ARB, CCB and THZ prevalent-users. We report calibrated hazard ratios (HRs) and their 95\% confidence intervals (CIs) across data sources. Grayed out entries do not pass study diagnostics.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}lrrrc@{}rrr}
    \hiderowcolors
    \toprule
    & & & \multicolumn{3}{c}{PS-stratified} & &  \multicolumn{3}{c}{PS-matched} \\
     \cmidrule(lr){4-6} \cmidrule(lr){8-10}
     & 
    & & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} &
      & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}

# Annotate

toString <- function(x) {
  ifelse(sapply(x, is.numeric),
         ifelse(x > 10,
                sprintf("%2.1f", x),
                sprintf("%1.2f", x)),
         x)
}

stratAnnotate <- function(x) {
  str <- toString(x)
  ifelse(wideTable$stratImbalanced > 0,
         paste0("{\\color{light-gray}", str, "}"),
         str)
}

matchAnnotate <- function(x) {
  str <- toString(x)
  ifelse(wideTable$matchImbalanced > 0,
         paste0("{\\color{light-gray}", str, "}"),
         str)
}

annotatedWideTable <- wideTable %>% 
  mutate(stratCalRr = stratAnnotate(stratCalRr),
         stratCalCi = stratAnnotate(stratCalCi),
         stratCalP = stratAnnotate(stratCalP)) %>%
  mutate(matchCalRr = matchAnnotate(matchCalRr),
         matchCalCi = matchAnnotate(matchCalCi),
         matchCalP = matchAnnotate(matchCalP))

stratIndex <- annotatedWideTable$stratCalRr == "NA"
annotatedWideTable$stratCalRr[stratIndex] <- "\\multicolumn{1}{c}{--}"
annotatedWideTable$stratCalCi[stratIndex] <- "\\multicolumn{1}{c}{--}"
annotatedWideTable$stratCalP[stratIndex] <- "\\multicolumn{1}{c}{--}"

matchIndex <- annotatedWideTable$matchCalRr == "NA"
annotatedWideTable$matchCalRr[matchIndex] <- "\\multicolumn{1}{c}{--}"
annotatedWideTable$matchCalCi[matchIndex] <- "\\multicolumn{1}{c}{--}"
annotatedWideTable$matchCalP[matchIndex] <- "\\multicolumn{1}{c}{--}"

annotatedWideTable <- annotatedWideTable %>% mutate(gap = "") %>%
  select(targetName, comparatorName, databaseId, outcomeId, stratCalRr, stratCalCi, stratCalP, stratImbalanced,
         gap, 
         matchCalRr, matchCalCi, matchCalP, matchImbalanced)

print(xtable(annotatedWideTable %>% filter(outcomeId == covidNarrowId) %>% 
               select(-outcomeId, -stratImbalanced, -matchImbalanced) %>%
               mutate(targetName = "", comparatorName = ""), 
             format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
 add.to.row = list(
        pos = as.list(c(0) * numDb),
        command = c(
          "                       \\multicolumn{10}{l}{Alpha-1 blocker vs 5ARI / PDE5} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\"
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ACE vs ARB} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\"          
          )
      ),      
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}

\clearpage

\definecolor{light-gray}{gray}{0.50}
\begin{table}[H]
 \caption{Relative risk of COVID-19 hospitalization for ACE inhibitors, ARB, CCB and THZ prevalent-users. We report calibrated hazard ratios (HRs) and their 95\% confidence intervals (CIs) across data sources. Grayed out entries do not pass study diagnostics.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}lrrrc@{}rrr}
    \hiderowcolors
    \toprule
    & & & \multicolumn{3}{c}{PS-stratified} & &  \multicolumn{3}{c}{PS-matched} \\
     \cmidrule(lr){4-6} \cmidrule(lr){8-10}
     & 
    & & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} &
      & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(annotatedWideTable %>% filter(outcomeId == hospitalizationId) %>% 
               select(-outcomeId, -stratImbalanced, -matchImbalanced) %>%
               mutate(targetName = "", comparatorName = ""), 
             format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
 add.to.row = list(
        pos = as.list(c(0) * numDb),
        command = c(
          "                       \\multicolumn{10}{l}{Alpha-1 blocker vs 5ARI / PDE5} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\"
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ACE vs ARB} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\"          
          )
      ),      
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}

\clearpage

\begin{table}[H]
 \caption{Relative risk of pneumonia for ACE inhibitors, ARB, CCB and THZ prevalent-users. We report calibrated hazard ratios (HRs) and their 95\% confidence intervals (CIs) across data sources. Grayed out entries do not pass study diagnostics.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}lrrrc@{}rrr}
    \hiderowcolors
    \toprule
    & & & \multicolumn{3}{c}{PS-stratified} & &  \multicolumn{3}{c}{PS-matched} \\
     \cmidrule(lr){4-6} \cmidrule(lr){8-10}
     & 
    & & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} &
      & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(annotatedWideTable %>% filter(outcomeId == intensiveServiceId) %>% 
               select(-outcomeId, -stratImbalanced, -matchImbalanced) %>%
               mutate(targetName = "", comparatorName = ""), 
             format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
 add.to.row = list(
        pos = as.list(c(0) * numDb),
        command = c(
          "                       \\multicolumn{10}{l}{Alpha-1 blocker vs 5ARI / PDE5} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\"
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\",
          # "\\rowcolor{white} \\\\ \\multicolumn{10}{l}{ACE vs ARB} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          # "                        & \\multicolumn{9}{l}{+ Combination} \\\\"          
          )
      ),      
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}

\clearpage

```{r, echo=FALSE, warning=FALSE}

design <- data.frame(
  databaseId = c(databaseIds, "Meta-analysis")
  # point = c(20, 20, 18, 20) # Seemingly unused
)

poorBalance <- "grey70"

table5 <- table %>% 
  left_join(design, by = "databaseId") %>% 
  filter(analysisId == 5) %>% 
  mutate(point = 21, size = 0.6) %>%
  mutate(color = ifelse(imbalanced > 0, poorBalance, "black")) %>%
  mutate(balanceColor = ifelse(imbalanced > 0, poorBalance, "black"))
table6 <- table %>% 
  left_join(design, by = "databaseId") %>% 
  filter(analysisId == 6) %>% 
  mutate(point = 21,size = 0.6) %>%
  mutate(color = ifelse(imbalanced > 0, "white", "white")) %>%
  mutate(balanceColor = ifelse(imbalanced > 0, poorBalance, "black"))

delta5 <- 0
delta6 <- 0

do56 <- TRUE
if (do56) {
  delta5 <- +0.25
  delta6 <- -0.25
}

pdf(file = "SixEffect.pdf", height = 10, width = 6)

dbs <- numDb

map <- function(index) {
  floor(index / dbs) + 2 * floor(index / (2 * dbs)) + 3 + index
}

tab <- table5 %>% filter(outcomeId == covidNarrowId) %>%
  mutate(index = row_number() - 1,
         row = map(index))

ymax <- max(tab$row)

par(mar = c(1,1,1,1))

plot(0,0, type = "n",
     ylim = c(-3, ymax),
     xlim = c(0, 12), axes = FALSE, 
     ylab = "", xlab = "")

textCex <- 0.6

cohortNames <- c("Alpha-1 blocker vs 5ARI / PDE5")
cohortPositions <- (c(1:length(cohortNames)) - 1) * (2 * dbs + 4) + 1
text(x = 0, y = ymax - cohortPositions, labels = cohortNames, pos = 4, cex = textCex)
# 
# minorNames <- rep(c("Monotherapy", "+ Combination"), length(cohortNames))
# minorTicks <- tab %>% filter(databaseId == "SIDIAP") %>% select(row) %>% pull() - 1
# text(x = 0.25, y = ymax - minorTicks, labels = minorNames, pos = 4, cex = textCex)

text(x = 0.5, y = ymax - tab$row, labels = tab$databaseId, pos = 4, cex = textCex)

start <- 3.5
width <- 2
spacer <- 2.4
tick <- 0.1

scaleMin <- 1/4  # -1
scaleMax <- 4    # +1

points(x = 4, y = ymax - 0.5, pch = 21, bg = "black")
text(x = 4.025, y = ymax - 0.5, labels = "PS-stratified", 
     pos = 4, cex = textCex, adj = 0.5)

points(x = 6, y = ymax - 0.5, pch = 21, bg = "white")
text(x = 6.025, y = ymax - 0.5, labels = "PS-matched", 
     pos = 4, cex = textCex, adj = 0.5)

points(x = 8, y = ymax - 0.5, pch = 22, bg = poorBalance, col = poorBalance)
text(x = 8.025, y = ymax - 0.5, labels = "Fails study diagnostics", 
     pos = 4, cex = textCex, adj = 0.5)

scale <- function(x) {
  log(x) / (log(scaleMax) - log(scaleMin)) * width
}

clip_min <- function(x) {
  pmax(x, -width / 2)
}

clip_max <- function(x) {
  pmin(x, +width / 2)
}

clip_rm <- function(x) {
  x[x > width / 2] <- NA
  x[x < -width / 2] <- NA
  x
}

library(wesanderson)

outcomeIds <- c(covidNarrowId, hospitalizationId, intensiveServiceId)
outcomeNames <- c("Diagnosis", "+ Hospital", "+ Intensive services")
outcomeColors <- c(wes_palette("Moonrise3")[5],
                   wes_palette("Moonrise2")[2],
                   wes_palette("Moonrise2")[3],
                   wes_palette("Moonrise3")[3])

designColors <- c(wes_palette("Moonrise2")[1],
                   wes_palette("Moonrise2")[2])
balancePointColor <- wes_palette("Moonrise2")[4]

outcomeColors <- adjustcolor(outcomeColors, alpha.f = 0.2)
designColors <- adjustcolor(designColors, alpha.f = 0.2)

for (i in 1:length(outcomeIds)) {

  offset <- start + (i - 1) * spacer

  rect(xleft = offset + scale(scaleMin),
       xright = offset + scale(scaleMax),
       ytop = ymax - 2,
       ybottom = -0.5,
       col = outcomeColors[i], #"grey90",
       border = NA)

  segments(x0 = offset, x1 = offset,
           y0 = -0.5, y1 = ymax - 2, lty = 3)

  # Stratification

  tab <- table5 %>% filter(outcomeId == outcomeIds[i]) %>%
    mutate(index = row_number() - 1,
           row = map(index))

  segments(x0 = offset + clip_min(scale(tab$calibratedCi95Lb)),
           x1 = offset + clip_max(scale(tab$calibratedCi95Ub)),
           y0 = ymax - tab$row + delta5, y1 = ymax - tab$row + delta5,
           col = tab$balanceColor)

  segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
           x1 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
           y0 = ymax - tab$row + tick + delta5,
           y1 = ymax - tab$row - tick + delta5,
           col = tab$balanceColor)

  segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
           x1 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
           y0 = ymax - tab$row + tick + delta5,
           y1 = ymax - tab$row - tick + delta5,
           col = tab$balanceColor)

  points(x = offset + clip_rm(scale(tab$calibratedRr)),
         y = ymax - tab$row + delta5,
         pch = tab$point,
         bg = tab$color,
         cex = tab$size,
         col = tab$balanceColor)

  if (do56) {

    # Matching
    tab <- table6 %>% filter(outcomeId == outcomeIds[i]) %>%
      mutate(index = row_number() - 1,
             row = map(index))

    segments(x0 = offset + clip_min(scale(tab$calibratedCi95Lb)),
             x1 = offset + clip_max(scale(tab$calibratedCi95Ub)),
             y0 = ymax - tab$row + delta6, y1 = ymax - tab$row + delta6,
             col = tab$balanceColor)

    segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
             x1 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
             y0 = ymax - tab$row + tick + delta6,
             y1 = ymax - tab$row - tick + delta6,
             col = tab$balanceColor)

    segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
             x1 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
             y0 = ymax - tab$row + tick + delta6,
             y1 = ymax - tab$row - tick + delta6,
             col = tab$balanceColor)

    points(x = offset + clip_rm(scale(tab$calibratedRr)),
           y = ymax - tab$row + delta6,
           pch = tab$point,
           bg = tab$color,
           cex = tab$size,
           col = tab$balanceColor)
  }

  # Bottom marks

  bt <- -0.75

  segments(x0 = offset - width / 2,
           x1 = offset + width / 2,
           y0 = bt, y1 = bt)

  marks <- scale(c(1/4, 1/2, 1, 2, 4))
  labels <- c("1/4", "1/2", "1", "2", "4")

  segments(x0 = offset + marks,
           x1 = offset + marks,
           y0 = bt,
           y1 = bt - 0.2)

  text(x = offset + marks,
       y = bt - 0.1,
       labels = labels,
       pos = 1, cex = textCex)

  text(x = offset,
       y = bt - 2,
       labels = outcomeNames[i],
       cex = 0.8)
}

invisible(dev.off())

```


\begin{figure}[H]
  \caption{Relative risk of COVID-19-related outcomes for ACE inhibitor, ARB, CCB and THZ prevalent-users.  
    Outcomes are COVID-19 diagnosis, COVID-19 hospitalization (+Hospital), patients hospitalized with pneumonia (PNA) and patients hospitalized with pneunomia, acute respiratory distree syndrome, acute kidney injury or sepsis (PAAS). 
    We plot calibrated hazard ratios (circles) and their 95% confidence intervals (wiskers) for both monotherapy and in-combination cohort definitions,
    labeled by propensity score (PS) adjustment method (black/white), across data sources.  Grayed out entries do not pass study diagnostics.}
    \vspace*{-0.25in}
  \centerline{
    \includegraphics[width=0.95\textwidth]{SixEffect}
  }
\end{figure}

# Min/max covariate counts across data sources

```{r, echo=FALSE, cache=FALSE}

countCovariate <- function (dataDir) {
  
  files <- list.files(file.path(dataDir, "shinyData"),
                    pattern = "covariate_balance_t\\d",
                    full.names = TRUE)
  
  counts <- do.call(
    "rbind.data.frame",
    lapply(files, function(file) {
      bal <- readRDS(file)
      t <- sub(".*t", "", file)
      target <- sub("_.*", "", t)
      c <- sub(".*c", "", file)
      comparator <- sub("_.*", "", c)
      return(list(rows = bal %>% filter(analysis_id == primaryAnalysisId,
                                        outcome_id == covidNarrowId) %>% nrow(),
                  target = as.numeric(target),
                  comparator = as.numeric(comparator)))
    }
  )
)
}
counts <- lapply(dataDirs, countCovariate)
names(counts) <- databaseIds
```

```{r, echo=FALSE}
for (databaseId in databaseIds) {
  count <- counts[[databaseId]]
  print(
    count %>% filter(rows == max(count$rows) | rows == min(count$rows)) %>%
    inner_join(cohorts, by = c("target" = "cohortId")) %>%
    rename(targetName = shinyName) %>%
    inner_join(cohorts, by = c("comparator" = "cohortId")) %>%
    rename(comparatorName = shinyName) %>%
    select(rows, targetName, comparatorName) %>% mutate(databaseId = databaseId) 
  )
}
```

# Important PS variables
```{r, echo=FALSE, cache=FALSE}

getTopPsCovariates <- function(studyFolder, databaseId, length = 25) {
  psModel <- readRdsCamelCase(file.path(studyFolder, "shinyData", paste0("propensity_model_", databaseId, ".rds")))
  covariate <- readRdsCamelCase(file.path(studyFolder, "shinyData", paste0("covariate_", databaseId, ".rds")))
  psModel <- psModel %>%
    left_join(covariate, by = c("databaseId", "analysisId", "covariateId")) %>% filter(analysisId == 5)
  psFreq <- psModel %>% count(covariateId, covariateName) %>% arrange(-n) %>% head(length)

  return(psFreq)
}
```

```{r, results="asis", echo = FALSE}
for (databaseId in databaseIds) {
  cat(sprintf("## %s \n\n", databaseId))
  freq <- getTopPsCovariates(dataDirs[[databaseId]], databaseId, length = 40)
  print(
    knitr::kable(freq, longtable = TRUE) %>% kableExtra::column_spec(2, width = "40em")
  )
}
```

# Balance plots

```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotCovariateBalanceScatterPlot <- function(balance, 
                                            beforeLabel = "Before stratification", 
                                            afterLabel = "After stratification",
                                            limits, yLimits,
                                            backgroundColor = "lightgrey",
                                            pointColor = rgb(0, 0, 0.8)) {
  
  if (missing(limits) || is.na(limits)) {
    limits <- c(min(c(balance$absBeforeMatchingStdDiff, balance$absAfterMatchingStdDiff),
                    na.rm = TRUE),
                max(c(balance$absBeforeMatchingStdDiff, balance$absAfterMatchingStdDiff),
                    na.rm = TRUE))
  }
  
  if (missing(yLimits) || is.na(yLimits)) {
    yLimits <- limits
  }
  theme <- ggplot2::element_text(colour = "#000000", size = 12)
  plot <- ggplot2::ggplot(balance, ggplot2::aes(x = absBeforeMatchingStdDiff, y = absAfterMatchingStdDiff)) +
    ggplot2::geom_point(color = adjustcolor(pointColor, alpha.f = 0.3), 
                        shape = 16, size = 2) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::geom_hline(yintercept = 0) +
    ggplot2::geom_vline(xintercept = 0) +
    ggplot2::scale_x_continuous(beforeLabel, limits = limits) +
    ggplot2::scale_y_continuous(afterLabel, limits = yLimits) +
    ggplot2::theme(text = theme,
                   axis.text.x = ggplot2::element_text(colour="black"),
                   axis.text.y = ggplot2::element_text(colour="black"),
                   panel.background = ggplot2::element_rect(fill = backgroundColor,
                                                            colour = backgroundColor,
                                                            size = 0.5, linetype = "solid"))
  return(plot)
}
```

## Across data sources

```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE}

library(cowplot)

getAllBalancePlots <- function(targetId, comparatorId, limits, yLimits) {

  balanceStrat <- lapply(databaseIds,
    function (databaseId) {
      plotCovariateBalanceScatterPlot(
        getCovariateBalance(NULL, targetId, comparatorId, analysisId = 5, outcomeId = covidNarrowId,
                            databaseId = databaseId, covariate = covariates[[databaseId]],
                            dataFolder = file.path(studyFolder, databaseId, "shinyData")),
        beforeLabel = "Before stratification", afterLabel = "After stratification", 
        limits = limits, yLimits = yLimits, backgroundColor = designColors[1], pointColor = balancePointColor
      )
    }
  )
  balanceMatch <- lapply(databaseIds,
    function (databaseId) {
      plotCovariateBalanceScatterPlot(
        getCovariateBalance(NULL, targetId, comparatorId, analysisId = 6, outcomeId = covidNarrowId,
                            databaseId = databaseId, covariate = covariates[[databaseId]],
                            dataFolder = file.path(studyFolder, databaseId, "shinyData")),
        beforeLabel = "Before matching", afterLabel = "After matching", 
        limits = limits, yLimits = yLimits, backgroundColor = designColors[2], pointColor = balancePointColor
      )
    }
  )
  return(list(strat = balanceStrat, match = balanceMatch))
}

saveAllBalancePlots <- function(balance, file) {
  
  labelPlots <- lapply(databaseIds,
    function (databaseId) {
      label <- paste0(databaseId, paste0(rep(" ", 12 - nchar(databaseId)), collapse = ""))
      ggplot2::ggplot() + 
        ggplot2::annotate("text", x = 0, y = 0, size = 6, angle = -90, label = label) +
        ggplot2::theme_void()
    }
  )
  plotList <- lapply(1:length(databaseIds),
                     function (i) list(balance$strat[[i]], balance$match[[i]], labelPlots[[i]]))
  plotList <- do.call(c, plotList)
  invisible(save_plot(file,
                      plot_grid(plotlist = plotList, ncol = 3, rel_widths = c(1, 1, 0.1)),
                      base_asp = 3 * 2/3, 
                      #ncol = 5,
                      base_height = 6))
}

balance <- getAllBalancePlots(alphaBlockerId, fiveAlphaId, limits = c(0, 0.6), yLimits = c(0, 0.2))
saveAllBalancePlots(balance, file = "allBalanceRasMono.pdf")
```


\begin{figure}[H]
  \caption{Covariate balance between ACE/ARB mono and CCB/THZ mono prevalent-user cohorts.  We plot balance before and after stratification and matching across data sources.}
  \centering{
    \includegraphics[width=0.9\textwidth]{allBalanceRasMono}
  }
\end{figure}
